---
title: "An overview of the functions in this package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{how_to_use_these_functions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

library(n3r)
library(dplyr)
library(tibble)
```

## vlookup 

This mimics Excel's `vlookup()` function - this is most handy when you just want to 'look up' one value from another dataframe. It's more intuitive than a join followed by dropping a bunch of columns. 

Consider a master dataframe with these variables.

```{r}
big <- mtcars %>% 
  rownames_to_column() %>% 
  rename(car = rowname)

big %>% 
  head()
```

Now suppose you only have 3 of these cars with `mpg` and `cyl` information. You want to `look up` the original dataframe and add a `disp` column.

```{r}
small <- big %>% 
  head(3) %>% 
  select(car, mpg, cyl)
small
```

You would typically do this, but we're saddled with several superfluous columns. 

```{r}
small %>% 
  left_join(big) 
```

Instead, we can do 

```{r}
small %>% 
  mutate(displacement = vlookup(this = car, df = big, key = 'car', value = 'disp'))
```

This is very fast because it runs on base R and it is clean and intuitive! 
